# Advanced modelling {#advanced}

## Batch

https://github.com/tidyverts/fable/wiki/Tidy-forecasting-with-the-fable-package

Estimating multiple models is a **key** feature of fable. Most time series can be naturally disaggregated using a series of factors known as keys. These keys are used to uniquely identify separate time series, each of which can be modelled separately.

```{r batch}
UKLungDeaths %>% 
  gather("sex", "deaths") %>% 
  model(ETS(deaths))
```


## Decomposition
https://github.com/tidyverts/fable/wiki/Combining-models

Objects which support a `components` method can then have their components modelled separately. The working name for this functionality is `model_components`, however a shorter (single word) verb is preferred.

The user should be able to specify how each of the components are modelled, and the `components` method should define how each component is combined (and perhaps some default models that can be used).

```{r decomp}
library(feasts)
md_decomp <- UKLungDeaths %>%
  STL(mdeaths ~ season(window = 12))
md_decomp
```
```{r decomp-plot, echo = FALSE}
md_decomp %>%
  gather(component, value) %>% 
  ggplot(aes(x = index, y = value)) + 
  geom_line() +
  facet_grid(component ~ ., scales = "free_y", switch = "y") + 
  theme_minimal() + 
  ylab(NULL)
```

```{r modelcomponents, eval = FALSE}
md_decomp %>% 
  model_components(???)
```

## Ensemble
https://github.com/tidyverts/fable/issues/34

## Boosting

## Reconciliation
https://github.com/tidyverts/fable/issues/36
